---
title: "Decision Tree on diabetes dataset"
output: html_notebook
---

Install and load libraries : mlr

```{r echo = T, results = 'hide'}
# install.packages("mlr", dependencies = TRUE)
```

Install and load libraries : tidyverse and mclust

```{r echo = T, results = 'hide'}
# install.packages("tidyverse")
# install.packages("mclust")
```

Load the diabetes data :

```{r}
data(diabetes, package = "mclust")
```

Use the installed libs :

```{r}
library(mlr)
library(tidyverse)
```

Format and display data : 

```{r}
diabetesTib <- as_tibble(diabetes)
diabetesTib
```

Get some stats of the data :

```{r}
summary(diabetesTib)
```

Plot the data around some of its classes :

```{r}
ggplot(diabetesTib, aes(glucose, insulin, col = class)) +
  geom_point()
```
```{r}
ggplot(diabetesTib, aes(sspg, insulin, col = class)) +
  geom_point()
```

```{r}
ggplot(diabetesTib, aes(glucose, sspg, col = class)) +
  geom_point()
```

Define a Task : 

```{r}
diabetesTask <- makeClassifTask(data = diabetesTib, target = "class")
diabetesTask

```

Define a learner : Recursive Partitioning Decision Tree

```{r}
rpart <- makeLearner('classif.rpart', predict.type="prob")
```

Train the model :

```{r}
rpartModel <- train(rpart, diabetesTask)
```

Use hold-out crossval :

```{r}
kfold <- makeResampleDesc("RepCV", folds = 10, reps = 50)
```

```{r}
kFoldCV <- resample(learner = rpart, task = diabetesTask, resampling = kfold)
```

Display the confusion matrix :

```{r}
calculateConfusionMatrix(kFoldCV$pred)
```
We can plot the decision tree :
```{r include=FALSE}
install.packages("rpart.plot", dependencies = TRUE)
```

```{r}
library("rpart.plot")
rpart.plot(getLearnerModel(rpartModel))
```

