---
title: "K Means Clustering on diabetes dataset"
output: html_notebook
---

Install and load libraries : mlr

```{r echo = T, results = 'hide'}
# install.packages("mlr", dependencies = TRUE)
```

Install and load libraries : tidyverse and mclust

```{r echo = T, results = 'hide'}
# install.packages("tidyverse")
# install.packages("mclust")
```

Load the diabetes data :

```{r}
data(diabetes, package = "mclust")
```

Use the installed libs :

```{r}
library(mlr)
library(tidyverse)
```

Format and display data : 

```{r}
diabetesTib <- as_tibble(diabetes)
diabetesTib
```

Get some stats of the data :

```{r}
summary(diabetesTib)
```
Keep the classes for visualisation purposes, remove them for the clustering part (unsupervised)

```{r}
diabetesTib_without_class <- select(diabetesTib, -class)
```


Plot the data around some of its classes :

```{r}
ggplot(diabetesTib, aes(glucose, insulin, col = class)) +
  geom_point()
```
```{r}
ggplot(diabetesTib, aes(sspg, insulin, col = class)) +
  geom_point()
```

```{r}
ggplot(diabetesTib, aes(glucose, sspg, col = class)) +
  geom_point()
```

Define a Task : 

```{r}
diabetesTask <- makeClusterTask(data = diabetesTib_without_class)
diabetesTask

```

Define a learner : K Means Clustering

```{r}
knn <- makeLearner("cluster.kmeans", centers = 3)
```

Train the model :

```{r}
knnModel <- train(knn, diabetesTask)
```

Get the predictions :

```{r}
pred <- predict(knnModel, task = diabetesTask)

```

Get some performance score results : we select these from the list below

"db" is Davies-Bouldin cluster separation measure
"G1" is Calinski-Harabasz pseudo F statistic
"G2" is Baker and Hubert adaptation of Goodman-Kruskal’s gamma statistic
"Silhouette" is Rousseeuw’s silhouette internal cluster quality index

```{r}
listMeasures("cluster")
```
Compute the scores from the predictions

```{r}
performance(pred, measures = list(db, G1, G2, silhouette), task = diabetesTask)
```

We can plot the clustering model :

```{r}
plotLearnerPrediction(learner = knn, task = diabetesTask)
```